Removing CO Interlopers from [\CII] Surveys With the Three Field Approach

### 2019-03-14 paper/ms.tex
Some random text

>>>>

\subsection{Three-Field Approach}\label{ssec:three_field}

Consider one of the interloping lines, and assume that there exists two other
lines emitted at the same redshift but by virtue of having a different
emission frequency have a different observed frequency. For example, CO(6-5)
emitted at $z=1$ will be observed at $345\,\GHz$, while CO(5-4) would be
observed at $288\,\GHz$ and CO(4-3) at $230\,\GHz$. As long as these
frequencies are in the observing band of some instrument, then we have enough
freedom to directly constrain the auto-spectrum of each line. We could proceed
as we did previously, forming suitable products and ratios to measure the
relevant cross-spectra \citep{2018arXiv181110609B},
\beq\label{eq:old_way}
P_{\text{CO(6-5),CO(6-5)}} = 
\frac{ \xps{\text{CO(6-5)}}{\text{CO(5-4)}} 
       \xps{\text{CO(4-3)}}{\text{CO(6-5)}} }
     { \xps{\text{CO(5-4)}}{\text{CO(4-3)}}}\text{.}
\eeq
However, this is a bit unconventional and extending to more than three lines
is cumbersome.
